How much is too much? Item Response Theory procedures to shorten tests

### 2025-02-13 sis2025/LaTex+Package/styles/paper-sis-template.tex
update sis

\section{Simulation study}
In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error ($1- d_i$ QUESTA è LA PROBABILITà DI NON CARELESS ERROR DEVO SPIEGARE MEGLIO, mi sto incansiandno basta che alla fine sia coerente), such that the more the items in a test, the higher the probability of committing careless mistakes. 
The careless error probability is instrinsically related to the rank of the item in the test, and it increases as the position of the item in the test increases. It increases exponentially with the function SCRIVERE LA FUNZIONE, such that the first administered item has $d_i = 1$ (i.e., does not have a probability of observing an incorrect response given the latent trait level $\theta$)

@@

>>>>

\section{Simulation study}
In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error ($1- d_i$ QUESTA è LA PROBABILITà DI NON CARELESS ERROR DEVO SPIEGARE MEGLIO, mi sto incansiandno basta che alla fine sia coerente), such that the more the items in a test, the higher the probability of careless error. 
The careless error probability is instrinsically related to the rank of the item in the test, and it increases as the position of the item in the test increases. It increases exponentially with the function SCRIVERE LA FUNZIONE, such that the first administered item has $d_i = 1$ (i.e., does not have a probability of observing an incorrect response given the latent trait level $\theta$).

The procedure is replicated 100 times. At each replica, a test of $B$ of 50 items with difficulty ($b_i \sim \mathcal{U}(-3, 3)$) discrimination ($a_i \sim \mathcal{U}(.90, 2)$) parameters drawn from uniform distributions is generated. Lucky 
guess and careless error parameters are constant, $c_i = 0, \forall i \in B$ and $d_i = 0, \forall i \in B$.
The $TIF^*$ is generated as the mean TIF of all items in $B$, which describes the ideal TIF that one would obtain if respondents are administered with all the items without getting tired.

A new test $B'$ is generated by keeping the item parameters equal to those in $B$, with the only exception of the careless error parameters, which are included as related to the rank of the item in the item bank with the function SCRIVERE LA FUNZIONE. 
The assumption is that the first administered item does not have a careless error probability ($d_{\text{1st}} = 1$) and it increases as the administration goes on. As such, the careless error probabilities associated to the second and third administered items are, respectively, $.99$ and $.98$. In this application, the maximum careless error probability associated to the last administered item is $.61$.

Frank and Léon are applied to generate a STF able to recreate the $TIF^*$. Both algorithm are applied considering the items in $B'$. While both algorithms are able to consider the careless error parameters in the computation of the IIFs, only Léon actually accounts for the number of items included in the STF. NON SO COSA STO DICENDO. devo controllare il codice perché ora non capisco. se anche frank calcola la iif considerando la careless error non capisco in che modo dovrebbe differenziarsi da leon ma effettivmente i risultati sono peggiori.

@@

\section{Results}

\begin{table}
	\centering
	\caption{\label{tab:summary} questa è una tabella, cominciamo}
	\begin{tabular}{l ccc}
		\hline
	Procedure	&	M			&	Min	&	Max	\\\hline
	All items	& $	0.07\pm	0.03$ &	$< 0.005$	&	0.13	\\
	Frank	& $	0.03	\pm	0.03	$ &	$<0.001$	&	0.14	\\
	Léon	& $	0.03	\pm	0.02	$ &	$<0.001$	&	0.1	\\
	\hline	
	\end{tabular}
\end{table}
